Equivalence Testing and the Second Generation P-Value

### 2018-08-28 manuscript.Rmd
Update manuscript.Rmd

As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below. In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8. We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of a meaningless SGPV in this range. This example suggests that the current implementation of the 'small sample correction' could be improved. If, on the other hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it might be preferable to simply never apply the 'small sample correction'.

>>>>

As a more extreme example of the peculiar behavior of the 'small sample correction' as currently implemented in the calculation of the SGPV see Figure \ref{fig:TOSTSGPV13} below. In this figure observed correlations (from a sample size of 10) from -1 to 1 are tested against an equivalence range from r = 0.4 to r = 0.8. We can see the SGPV has a peculiar shape because it is set to 0.5 for certain observed correlations, even though there is no risk of 'misleading' values in this range. This example suggests that the current implementation of the 'small sample correction' could be improved. If, on the other hand, the SGPV is mainly meant to be interpreted when it is 0 or 1, it might be preferable to simply never apply the 'small sample correction'.
